---
title: "Example .docx Report"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example .docx Report}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  out.width = "150%"
)
```

```{=html}
<style>

.tabset-pills .tab-content {
    border: 0px;
}

</style>
```
These example reports were rendered to `.docx` files and then converted to PDFs for web publishing.

After rendering to `.docx`, the file was opened in Microsoft Word for manual formatting edits:

-   Change images to float around text.
-   Some wide tables should be `autofit` by going to `Layout` \> `AutoFit` \> `AutoFit Window`.
-   Adjust plot sizes and page breaks.

The below examples show the output with and without these edits.

##  {.tabset .tabset-pills}

### Manual Formatting Edits

See this manually formatted report full screen in a [new tab](https://rawcdn.githack.com/WA-Department-of-Agriculture/soils/944448976992604a12dafbf47258327be0e5ab98/inst/example_reports/example_producer_report.pdf "See the manually edited .docx report without edits in full screen."){target="_blank"}.

```{r}
knitr::include_url("https://rawcdn.githack.com/WA-Department-of-Agriculture/soils/944448976992604a12dafbf47258327be0e5ab98/inst/example_reports/example_producer_report.pdf", height = "500px")
```

### Without Edits

See the original rendered report full screen in a [new tab](https://rawcdn.githack.com/WA-Department-of-Agriculture/soils/72aefb3a55da25b6b1d3191c45ebc90570555e7d/inst/example_reports/example_producer_report_notFormatted.pdf "See the original .docx report without edits in full screen."){target="_blank"}.

```{r}
knitr::include_url("https://rawcdn.githack.com/WA-Department-of-Agriculture/soils/72aefb3a55da25b6b1d3191c45ebc90570555e7d/inst/example_reports/example_producer_report_notFormatted.pdf", height = "500px")
```
