---
title: "Example reports"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example reports}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# HTML

HTML reports contain interactive features such as a table of contents, map, figures, and a downloadable spreadsheet. These reports are 'self-contained', meaning all images and necessary resources are embedded in the file. Consequently, the file size can be quite large.

These reports can be distributed with cloud storage (Google Drive, Box.com, Dropbox.com, etc.). Report recipients must download the `.html` file to their computer and then open the file in their web browser.

Open this report in a [new tab](https://htmlpreview.github.io/?https://github.com/WA-Department-of-Agriculture/soils/blob/44d493360e987f4ae1d6ae7cd6de5beafd045f4d/inst/example_reports/producer_report.html){target="_blank"}.

```{r echo=FALSE, out.width="100%"}
knitr::include_url(
  "https://htmlpreview.github.io/?https://github.com/WA-Department-of-Agriculture/soils/blob/44d493360e987f4ae1d6ae7cd6de5beafd045f4d/inst/example_reports/producer_report.html", 
  height = "500px")
```

# MS Word

This example report was rendered to a `.docx` file and then converted to a PDF for web publishing.

Open this report in a [new tab](https://drive.google.com/file/d/15M0HfRbyjUxdkMPib71NdfBB5yKWgVfW/preview){target="_blank"}.

<object style="width:100%;height:500px" data="https://drive.google.com/file/d/15M0HfRbyjUxdkMPib71NdfBB5yKWgVfW/preview">

<p>Oops! Your browser doesn't seem to support embedded PDFs.</p>

<p><a href="https://drive.google.com/file/d/15M0HfRbyjUxdkMPib71NdfBB5yKWgVfW/preview">Try downloading it instead.</a></p>

</object>
