---
title: "Example reports"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example reports}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# HTML

HTML reports contain interactive features such as a table of contents, map,
figures, and a downloadable spreadsheet. These reports are "self-contained" and
embed all dependencies in the HTML file. As a result, the file size can be quite
large.

These reports can be distributed with cloud storage (Google Drive, Box.com,
Dropbox.com, etc.). Report recipients must download the `.html` file to their
computer and then open the file in their web browser.

Open this report in a [new
tab](https://soils-example-html.netlify.app/){target="_blank"}.

```{r echo=FALSE, out.width="100%"}
knitr::include_url(
  "https://soils-example-html.netlify.app/", height = "500px")
```

# MS Word

This example report was rendered to a `.docx` file and then converted to a PDF
for web publishing.

Open this report in a [new
tab](https://drive.google.com/file/d/15M0HfRbyjUxdkMPib71NdfBB5yKWgVfW/preview){target="_blank"}.

<object style="width:100%;height:500px" data="https://drive.google.com/file/d/15M0HfRbyjUxdkMPib71NdfBB5yKWgVfW/preview">

<p>Oops! Your browser doesn't seem to support embedded PDFs.</p>

<p><a href="https://drive.google.com/file/d/15M0HfRbyjUxdkMPib71NdfBB5yKWgVfW/preview">Try
downloading it instead.</a></p>

</object>
